Online Verification of Commutativity

### 2020-08-14 acmPaper/paper.tex

We implemented a system for interfacing with the optimal set incremental checker in Gator \xxx[dg]{Which algorithm was it?}.  Gator uses TypeScript for CPU computations, so it was reasonable to build a system to manage graphs for interoperation with the path independence algorithm.

Using this algorithm, we found a bug in the reflection model, where a matrix was not being divided correctly by its determinant \xxx[dg]{List other things I find, if anything}.  We also inserted previous bugs to check the algorithm was working correctly, and it identified all inserted bugs.

>>>>

We implemented a system for interfacing with the optimal set incremental checker in Gator \xxx[dg]{Which algorithm was it?}\xxx[AK]{\ref{algo_online_minimal}}.  Gator uses TypeScript for CPU computations, so it was reasonable to build a system to manage graphs for interoperation with the path independence algorithm.

Using this algorithm, we found a bug in the reflection model, where a matrix was not being divided correctly by its determinant \xxx[dg]{List other things I find, if anything}\xxx[ak]{I think it may be nice to add more detail for at least one bug (code, what was the program doing, what the graph/conflict was, time taken, etc.)}.  We also inserted previous bugs to check the algorithm was working correctly, and it identified all inserted bugs.
